Unity in diversity: Children from 17 diverse communities process gaze in similar ways

### 2024-03-19 supplement/supplement.Rmd
clean repo

```{r figpred1, include = T, fig.align = "center", fig.cap = "A) Age distribution and B) prevalence of different types of technology by community. Left: dots show individual data points. Right: color shows the proportion of children with access to screens or touchscreens.", out.width="100%"}
# techpred <- plot_grid(page, ppred, rel_widths = c(1, 0.5),align = "h", labels = c("A", "B"))
# 
# ggsave(plot = techpred, "../visuals/techpred.png",  height = 7, width = 10, scale = 1)

knitr::include_graphics("../visuals/techpred.png")

@@

# dempred_agg <- data%>%
#   group_by(community)%>%
#   distinct(subjid, .keep_all = T)%>%
#   select(subjid, community, continent, children, younger_children, household)%>%
#   pivot_longer(names_to = "dem", values_to = "value", cols = c(children, younger_children, household))%>%
#     mutate(dem = recode(dem,
#                       younger_children = "younger children"),
#          dem = factor(dem, levels = c("household", "children", "younger children")))%>%
#   group_by(community, dem)%>%
#   na.omit()%>%
#   tidyboot_mean(col = value)
#   
# 
# dempred <- data%>%
#   group_by(community)%>%
#   distinct(subjid, .keep_all = T)%>%
#   select(subjid, community, continent, children, younger_children, household)%>%
#   pivot_longer(names_to = "dem", values_to = "value", cols = c(children, younger_children, household))%>%
#   mutate(dem = recode(dem,
#                       younger_children = "younger children"),
#          dem = factor(dem, levels = c("household", "children", "younger children")))%>%
#   ggplot(aes(y = value, x = community))+
#   facet_grid(dem~., scales = "free", space = "free_x")+
#   geom_jitter(width = 0.2, height = 0.1, alpha = 0.1)+
#   geom_pointrange(data = dempred_agg, aes(ymin = ci_lower, ymax = ci_upper, y = mean), col = "firebrick")+
#   theme_few()+
#   labs(y = "No. of individuals", x= "")+
#   theme(axis.text.x = element_text(angle = 55, vjust = 1, hjust=1))
# 
# ggsave(plot = dempred, "../visuals/dempred.png", height = 6, width = 10, scale = 1)

knitr::include_graphics("../visuals/dempred.png")

@@

```{r task, include = T, fig.align = "center", fig.cap = "Screenshot from the task. The scene depicts the choice phase in a test trial. Participants had to use the gaze of the agent to locate the balloon and click on the hedge where they thought the balloon was.", out.width="80%"}
knitr::include_graphics("../visuals/task.png")
```

@@

```{r figagents, include = T, fig.align = "center", fig.cap = "Agents used in the task. Some agents were used for multiple cultural settings", out.width="100%"}
knitr::include_graphics("../visuals/agents.png")
```

@@

# pdraws <- readRDS("../saves/pdraws.rds")%>%
#   mutate(type = recode(type,
#                        ageinyears = "Age",
#                        targetcentrality = "Target centrality"),
#          type = factor(type, levels = c("Age","Target centrality")))
# 
# 
# 
# ppred <- ggplot(pdraws, aes(x= post, y = community))+
#   geom_density_ridges(col = "white", alpha = .75, fill = "grey")+
#   geom_vline(xintercept = 0, lty = 3)+
#   facet_grid(~type, scales = "free", space = "free_y")+
#   #stat_pointinterval(size = 0.1)+
#   #xlim(-0.15, 0.1)+
#   labs(x = "Posterior model estimate", y= "")+
#   theme_few()+
#   theme( strip.text.y.right = element_text(angle = 0))
# 
# 
# ggsave(plot = ppred, "../visuals/pred.png", height = 6, width = 12, scale = 1)

knitr::include_graphics("../visuals/pred.png")

@@

# pvis_pred <- plot_grid(
# plot_grid(
#   pagg_dev, pind, rel_widths = c(1,1.5), align = "h", axis = "bt",labels = c("A", "B")
# ),
# plot_grid(
#   ptagg, ptind, rel_widths = c(1,1.5), align = "h", axis = "bt", labels = c("C", "D")
# ), nrow = 2, align = "v"
# )
# 
# ggsave(plot = pvis_pred, "../visuals/pvis_pred.png", width = 12, height = 8, bg = "white", scale = 1.25)

knitr::include_graphics("../visuals/pvis_pred.png")

@@

# ptc_com <- readRDS("../saves/ptc_com.rds")
# 
# pcomtc <- ggplot(ptc_com,aes(x = touchscreen, y = Estimate))+
#   stat_cor(aes(x = touchscreen, y = Estimate,label = paste(..r.label..)),inherit.aes = F,r.accuracy = 0.01, cor.coef.name = "r",label.y = 0.85)+
#   geom_point(alpha = .75, pch = 1)+
#   geom_smooth(method = "lm", col = "firebrick", alpha = .25)+
#   labs(x = "Touchscreen exposure", y = "Relative imprecision (age corrected)")+
#   theme_few()
# 
# ggsave(plot = pcomtc, "../visuals/pcomtc.png", height = 4, width = 5, scale = 1.2)

knitr::include_graphics("../visuals/pcomtc.png")
```

>>>>

```{r figpred1, include = T, fig.align = "center", fig.cap = "A) Age distribution and B) prevalence of different types of technology by community. Left: dots show individual data points. Right: color shows the proportion of children with access to screens or touchscreens.", out.width="100%"}
# techpred <- plot_grid(page, ppred, rel_widths = c(1, 0.5),align = "h", labels = c("A", "B"))
# 
# ggsave(plot = techpred, "../figures/techpred.png",  height = 7, width = 10, scale = 1)

knitr::include_graphics("../figures/techpred.png")

@@

# dempred_agg <- data%>%
#   group_by(community)%>%
#   distinct(subjid, .keep_all = T)%>%
#   select(subjid, community, continent, children, younger_children, household)%>%
#   pivot_longer(names_to = "dem", values_to = "value", cols = c(children, younger_children, household))%>%
#     mutate(dem = recode(dem,
#                       younger_children = "younger children"),
#          dem = factor(dem, levels = c("household", "children", "younger children")))%>%
#   group_by(community, dem)%>%
#   na.omit()%>%
#   tidyboot_mean(col = value)
#   
# 
# dempred <- data%>%
#   group_by(community)%>%
#   distinct(subjid, .keep_all = T)%>%
#   select(subjid, community, continent, children, younger_children, household)%>%
#   pivot_longer(names_to = "dem", values_to = "value", cols = c(children, younger_children, household))%>%
#   mutate(dem = recode(dem,
#                       younger_children = "younger children"),
#          dem = factor(dem, levels = c("household", "children", "younger children")))%>%
#   ggplot(aes(y = value, x = community))+
#   facet_grid(dem~., scales = "free", space = "free_x")+
#   geom_jitter(width = 0.2, height = 0.1, alpha = 0.1)+
#   geom_pointrange(data = dempred_agg, aes(ymin = ci_lower, ymax = ci_upper, y = mean), col = "firebrick")+
#   theme_few()+
#   labs(y = "No. of individuals", x= "")+
#   theme(axis.text.x = element_text(angle = 55, vjust = 1, hjust=1))
# 
# ggsave(plot = dempred, "../figures/dempred.png", height = 6, width = 10, scale = 1)

knitr::include_graphics("../figures/dempred.png")

@@

```{r task, include = T, fig.align = "center", fig.cap = "Screenshot from the task. The scene depicts the choice phase in a test trial. Participants had to use the gaze of the agent to locate the balloon and click on the hedge where they thought the balloon was.", out.width="80%"}
knitr::include_graphics("../figures/task.png")
```

@@

```{r figagents, include = T, fig.align = "center", fig.cap = "Agents used in the task. Some agents were used for multiple cultural settings", out.width="100%"}
knitr::include_graphics("../figures/agents.png")
```

@@

# pdraws <- readRDS("../saves/pdraws.rds")%>%
#   mutate(type = recode(type,
#                        ageinyears = "Age",
#                        targetcentrality = "Target centrality"),
#          type = factor(type, levels = c("Age","Target centrality")))
# 
# 
# 
# ppred <- ggplot(pdraws, aes(x= post, y = community))+
#   geom_density_ridges(col = "white", alpha = .75, fill = "grey")+
#   geom_vline(xintercept = 0, lty = 3)+
#   facet_grid(~type, scales = "free", space = "free_y")+
#   #stat_pointinterval(size = 0.1)+
#   #xlim(-0.15, 0.1)+
#   labs(x = "Posterior model estimate", y= "")+
#   theme_few()+
#   theme( strip.text.y.right = element_text(angle = 0))
# 
# 
# ggsave(plot = ppred, "../figures/pred.png", height = 6, width = 12, scale = 1)

knitr::include_graphics("../figures/pred.png")

@@

# pvis_pred <- plot_grid(
# plot_grid(
#   pagg_dev, pind, rel_widths = c(1,1.5), align = "h", axis = "bt",labels = c("A", "B")
# ),
# plot_grid(
#   ptagg, ptind, rel_widths = c(1,1.5), align = "h", axis = "bt", labels = c("C", "D")
# ), nrow = 2, align = "v"
# )
# 
# ggsave(plot = pvis_pred, "../figures/pvis_pred.png", width = 12, height = 8, bg = "white", scale = 1.25)

knitr::include_graphics("../figures/pvis_pred.png")

@@

# ptc_com <- readRDS("../saves/ptc_com.rds")
# 
# pcomtc <- ggplot(ptc_com,aes(x = touchscreen, y = Estimate))+
#   stat_cor(aes(x = touchscreen, y = Estimate,label = paste(..r.label..)),inherit.aes = F,r.accuracy = 0.01, cor.coef.name = "r",label.y = 0.85)+
#   geom_point(alpha = .75, pch = 1)+
#   geom_smooth(method = "lm", col = "firebrick", alpha = .25)+
#   labs(x = "Touchscreen exposure", y = "Relative imprecision (age corrected)")+
#   theme_few()
# 
# ggsave(plot = pcomtc, "../figures/pcomtc.png", height = 4, width = 5, scale = 1.2)

knitr::include_graphics("../figures/pcomtc.png")
```
